To Ship or Not to Ship: Explict Temporal Ratios Lead to Impatience

### 2015-12-15 paper/paperintro.tex
Now with properly formatted table

%\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{graphicx}
\usepackage{booktabs,caption,fixltx2e}
%opening
\title{To Ship or Not to Ship: Explict Temporal Ratios Lead to Impatience}
\author{Daniel Wall}

@@

This work aims to demonstrate that the fourth research stream -- that patience is affected by how options are framed -- can affect real world phenomenon.
Specifically, this paper combines the work of \citeA{Read2013} -- which shows that framing amounts as ratios alters patience -- and \citeA{MarzilliEricson2015} -- which shows that people rely on differences and ratios in standard intertemporal frame as well as the work  of  \citeA{Read2005} which shows that how times are framed can alter patience. 
Specifically, I focus on how framing times as ratios can decrease patience.
When delays are sufficiently small, and when temporal ratios are made explicit, our attention will be focused on the ratio of how much \textit{longer} we will wait. 
For instance reframing a choice between ``receiving \$100  in 1 day'' and ``\$110 in 10 days'' to being a choice between ``receiving \$100  in 1 day'' and ``\$110 in 10 \textit{times as long}'', will focus participants on how much longer they will wait for \$110 as opposed to receiving the \$100 today.
This increased focus on how long they will wait, leads to decreased patience when times are framed as ratios.

@@

\textit{Hypothesis 1} In gain intertemporal choices, when times are expressed as ratios, people will be more impatient than when expressed as delays.

@@

\textit{Hypothesis 2} In loss intertemporal choices, when times are expressed as ratios, people will be more impatient than when expressed as delays.

@@

\textit{Hypothesis 3} In shipping scenarios, when times are expressed as ratios, people will be more impatient than when expressed as delays.

I test these hypotheses across three studies.
Study 1 investigates Hypothesis 1 by making temporal ratios explicit in intertemporal.

@@

\section{Study 1}
In study 1 participants chose between smaller sooner and larger later options. 
These options were displayed in one of two frames: implicit temporal ratios and explicit temporal ratios. 
Study 1 tests Hypothesis 1 above

@@

>>>>

%\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{graphicx}
\usepackage{booktabs,caption,fixltx2e}
\usepackage{rotating}
\usepackage[letterpaper, margin=1in]{geometry}

\usepackage{pdflscape}

%opening
\title{To Ship or Not to Ship: Explict Temporal Ratios Lead to Impatience}
\author{Daniel Wall}

@@

This work aims to demonstrate that the fourth research stream -- that patience is affected by how options are framed -- can affect real world phenomenon.
Specifically, this paper combines the work of \citeA{Read2013} -- which shows that framing amounts as ratios alters patience -- and \citeA{MarzilliEricson2015} -- which shows that people rely on differences and ratios in standard intertemporal frame as well as the work  of  \citeA{Read2005} which shows that how times are framed can alter patience.

Specifically, I focus on how framing times as ratios can decrease patience.
When delays are sufficiently small, and when temporal ratios are made explicit, our attention will be focused on the ratio of how much \textit{longer} we will wait. 
For instance reframing a choice between ``receiving \$100  in 1 day'' and ``\$110 in 10 days'' to being a choice between ``receiving \$100  in 1 day'' and ``\$110 in 10 \textit{times as long}'', will focus participants on how much longer they will wait for \$110 as opposed to receiving the \$100 today.
This increased focus on how long they will wait, leads to decreased patience when times are framed as ratios.

@@

\textit{Hypothesis 1:} In gain intertemporal choices, when times are expressed as ratios, people will be more impatient than when expressed as delays.

@@

\textit{Hypothesis 2:} In loss intertemporal choices, when times are expressed as ratios, people will be more impatient than when expressed as delays.

@@

\textit{Hypothesis 3:} In shipping scenarios, when times are expressed as ratios, people will be more impatient than when expressed as delays.

I test these hypotheses across three studies.
Study 1 tests Hypothesis 1 by making temporal ratios explicit in intertemporal choices.

@@

\section{Study 1}
In study 1 participants chose between smaller sooner and larger later options. 
These options were displayed in one of two frames: implicit temporal ratios and explicit temporal ratios. 
Study 1 tests Hypothesis 1: In gain intertemporal choices, when times are expressed as ratios, people will be more impatient than when expressed as delays.

@@

\begin{landscape}
\begin{table}[!ht]
	\caption{Amounts and times of Stimuli for Studies 1-3} \label{tab:stimuli}
	\includegraphics[]{Stimuli_For_Study.pdf}
\end{table}
\end{landscape}
